Network Slicing and Resource Allocation in an Open RAN System \vspace{-.1cm}

### 2021-09-29 Latex/journal_v1/V7/pr.tex
add paper

\begin{figure}
  \centering
    \includegraphics[scale = 0.4]{draw1.pdf}
  \caption{Network sliced ORAN system}
  \label{fig:c11}
\end{figure}

@@

In addition, there are $R$ multi-antenna RU that are shared between slices. Each RU $r \in \{1,2,...,R \}$
has $J$ antenna for transmitting and receiving data. Moreover, all RUs, have access to PRBs.
\subsection{The Achievable Rate}
The SNR of $i^{th}$ UE requesting served at slice $s$ on PRB $k$ is obtained from
\begin{equation}\label{eq2}
\rho_{r,u(s,i)}^{k} =  \frac{|p_{r,u(s,i)}^{k}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0 + I_{r,u(s,i)}^{k}},
\end{equation} 
where $p_{r,u(s,i)}^{k}$ represents the transmission power from o-RU $r$ to $i^{th}$ UE served at slice $s$ on PRB $k$. 
${\bold{h}_{r,u(s,i)}^{k}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 
$r^{th}$ RU to the $i^{th}$ UE in $s^{th}$ slice. In addition, $\bold{w}_{r,u(s,i)}^{k} \in \mathbb{C}^{J}$ depicts the  transmit beamforming vector from $r^{th}$ RU to the $i^{th}$ UE in $s^{th}$ slice that is the zero forcing beamforming vector to minimize the interference which is indicated as below
\begin{equation}
\bold{w}_{r,u(s,i)}^{k} = {\bold{h}_{r,u(s,i)}^{k}}({\bold{h}_{r,u(s,i)}^{H \: k}} {\bold{h}_{r,u(s,i)}^{k}})^{-1}
\end{equation}
Moreover, $g_{u(s,i)}^r \in \{0,1\}$ is a binary variable that illustrates whether RU $r$ is mapped to the $i^{th}$ UE allocate to $s^{th}$ slice or not. 
Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u(s,i)}^{k}$ is the power of interfering signals represented as follow
\begin{equation}
\begin{split}
I_{r,u(s,i)}^{k} &=
 \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} \gamma_{1}  p_{u(s,i)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,i)}^{k} g_{u(s,i)}^{r'}|^2}_{\text{(intra-slice interference)}}\\
&+ \underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} \gamma_{2}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
\end{split}
\end{equation}
where $\gamma_{1} = e^{k}_{r,u(s,i)}e^{k}_{r',u(s,l)}a_{u(s,i)}a_{u(s,l)}$
and $\gamma_{2} = e^{k}_{r,u(s,i)}e^{k}_{r',u(n,l)}a_{u(s,i)}a_{u(y,l)}$.
Where $a_{u(s,i)} \in \{0,1\}$ is a binary variable to depict user admission.
$e^{k}_{r,u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ o-RU.

The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as $\mathcal{R}_{u(s_1,i)}^{e}$.
\begin{equation}\label{eq1}
\begin{split}
\mathcal{R}_{u(s_1,i)}^{e,r} &= \sum_{k=1}^{K_{s_1}} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}})a_{u(s_1,i)} e^k_{r,u(s_1,i)},\\
\mathcal{R}_{u(s_1,i)}^{e} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_1,i)}^{e,r} 
\end{split}
\end{equation}
where $B$ is the bandwidth of system. 
$\mathcal{R}_{u(s_1,i)}^{e,r}$ is the achievable rate of each RU $r$ to UE $i$ in slice $s_1$.
Since the blocklength in URLLC is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{2}^{th}$ application of service type 2 (URLLC) is not achieved from Shannon Capacity formula. So, for the short packet transmission the achievable data rate is approximated from follow
\begin{equation}\label{eq11}
\begin{split}
\mathcal{R}_{u(s_2,i)}^{u,r} &= \sum_{k=1}^{K_{s_2}} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_2,i)}^{k}){\beta}_{u(s_2,i)}^{k}\\
\mathcal{R}_{u(s_1,i)}^{e} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_2,i)}^{e,r} 
\end{split}
\end{equation}
Where ${\beta}_{u(s_2,i)}^{k}=a_{u(s_2,i)} e^{k}_{u(s_2,i)}$
and $\zeta_{u(s_2,i)}^{k} = log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{C_{u(s_2,i)}^{k}}{N_{u(s_2,i)}^{k}}})$
Where, $\epsilon $ is the transmission probability, $Q^{-1}$ is the inverse of Q- function (Gaussian),
$C_{u(s_2,i)}^{k} = 1 - \frac{1}{(1+\rho_{u(s_2,i)}^{k})}$ depicts the channel dispersion of UE  $i$ at slice $s_2$, experiencing PRB $k$ and
$N_{u(s_2,i)}^{k}$ represents the blocklength of it. 
$\mathcal{R}_{u(s_1,i)}^{e,r}$ is the achievable rate of each RU $r$ to UE $i$ in slice $s_2$.
\subsection{Mean Delay}
In this part, the end to end mean delay for a service is obtained.
Suppose the mean total delay is depicted as $T_{tot}$.
\begin{equation}
\begin{split}
T_{tot} &=  T_{process} + T_{transmission} + T_{propagation}\\
T_{process} &=  T_{RU} + T_{DU} + T_{CU} + T_{UPF}\\
T_{transmission} &= T_{front} + T_{mid} + T_{back} + T_{trans2net} \\
T_{propagation} &= T_{front} + T_{mid} + T_{back} + T_{trans2net} \\
\end{split}
\end{equation}
%T_{tot} = T_{RU} + T_{front} + T_{DU} + T_{mid} + T_{CU} + T_{back} + T_{core} + T_{trans2net}
Total delay is sum of processing delay, transmission delay and propagation delay. 
The propagation delay is the time takes for a signal to reach to its destination. So it has a constant value based on the length of fiber link ($T = L/c$, where $L$ is the length of link and c is the speed of signal).
Here we assume the value of propagation delay is negligible compared to the rest.
\subsubsection{Processing Delay}
Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u(s,i)}$ for the $i^{th}$ UE of the $s^{th}$ slice.
Therefore, the mean arrival data rate of the $s^{th}$ slice in the UPF layer is $\alpha_{s}^1 = \sum_{u=1}^{U_s}a_{u(s,i)}\lambda_{u(s,i)}$, where $a_{u(s,i)}$ is a binary variable which indicates whether the $i^{th}$ UE requested $s^{th}$ service is admitted or not.

@@

@@

Power of each O-RU is obtained as below
P_r =  \sum_{s=1}^{S} \sum_{i=1}^{U_v} \sum_{k=1}^{K_s}p_{r,u(s,i)}^{k}a_{u(s,i)} e^{k}_{r,u(s,i)}g_{u(s,i)}^r.

>>>>

@@

In addition, there are $R$ multi-antenna RU that are shared between slices. Each RU $r \in \{1,2,...,R \}$
has $J$ antenna for transmitting and receiving data. Moreover, all RUs, have access to PRBs.
\subsection{The Achievable Rate}
The SNR of $i^{th}$ UE requesting served at slice $s$ on PRB $k$ is obtained from
\begin{equation}\label{eq2}
\rho_{r,u(s,i)}^{k} =  \frac{|p_{r,u(s,i)}^{k}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0},
\end{equation} 
where $p_{r,u(s,i)}^{k}$ represents the transmission power from o-RU $r$ to $i^{th}$ UE served at slice $s$ on PRB $k$. 
${\bold{h}_{r,u(s,i)}^{k}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 
$r^{th}$ RU to the $i^{th}$ UE in $s^{th}$ slice. In addition, $\bold{w}_{r,u(s,i)}^{k} \in \mathbb{C}^{J}$ depicts the  transmit beamforming vector from $r^{th}$ RU to the $i^{th}$ UE in $s^{th}$ slice that is the zero forcing beamforming vector to minimize the interference which is indicated as below
\begin{equation}
\bold{w}_{r,u(s,i)}^{k} = {\bold{h}_{r,u(s,i)}^{k}}({\bold{h}_{r,u(s,i)}^{H \: k}} {\bold{h}_{r,u(s,i)}^{k}})^{-1}
\end{equation}
Moreover, $g_{u(s,i)}^r \in \{0,1\}$ is a binary variable that illustrates whether RU $r$ is mapped to the $i^{th}$ UE allocate to $s^{th}$ slice or not. 
Also, $BN_0$ denotes the power of Gaussian additive noise.
Also, $a_{u(s,i)} \in \{0,1\}$ is a binary variable to depict user admission.
$e^{k}_{r,u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ o-RU.

The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as $\mathcal{R}_{u(s_1,i)}^{e}$.
\begin{equation}\label{eq1}
\begin{split}
\mathcal{R}_{u(s_1,i)}^{e,r} &= \sum_{k=1}^{K_{s_1}} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}})a_{u(s_1,i)} e^k_{r,u(s_1,i)},\\
\mathcal{R}_{u(s_1,i)}^{e} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_1,i)}^{e,r} 
\end{split}
\end{equation}
where $B$ is the bandwidth of system. 
$\mathcal{R}_{u(s_1,i)}^{e,r}$ is the achievable rate of each RU $r$ to UE $i$ in slice $s_1$.
Since the blocklength in URLLC is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{2}^{th}$ application of service type 2 (URLLC) is not achieved from Shannon Capacity formula. So, for the short packet transmission the achievable data rate is approximated from follow
\begin{equation}\label{eq11}
\begin{split}
\mathcal{R}_{u(s_2,i)}^{u,r} &= \sum_{k=1}^{K_{s_2}} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_2,i)}^{k}){\beta}_{u(s_2,i)}^{k}\\
\mathcal{R}_{u(s_1,i)}^{e} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_2,i)}^{e,r} 
\end{split}
\end{equation}
Where ${\beta}_{u(s_2,i)}^{k}=a_{u(s_2,i)} e^{k}_{u(s_2,i)}$
and $\zeta_{u(s_2,i)}^{k} = log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{C_{u(s_2,i)}^{k}}{N_{u(s_2,i)}^{k}}})$
Where, $\epsilon $ is the transmission probability, $Q^{-1}$ is the inverse of Q- function (Gaussian),
$C_{u(s_2,i)}^{k} = 1 - \frac{1}{(1+\rho_{u(s_2,i)}^{k})}$ depicts the channel dispersion of UE  $i$ at slice $s_2$, experiencing PRB $k$ and
$N_{u(s_2,i)}^{k}$ represents the blocklength of it. 
$\mathcal{R}_{u(s_1,i)}^{e,r}$ is the achievable rate of each RU $r$ to UE $i$ in slice $s_2$.
\subsection{Mean Delay}
In this part, the end to end mean delay for a service is obtained.
Suppose the mean total delay is depicted as $T_{tot}$.
\begin{equation}
\begin{split}
T_{tot} &=  T_{process} + T_{transmission} + T_{propagation}\\
T_{process} &=  T_{RU} + T_{DU} + T_{CU} + T_{UPF}\\
T_{transmission} &= T_{front} + T_{mid} + T_{back} + T_{trans2net} \\
T_{propagation} &= T_{front} + T_{mid} + T_{back} + T_{trans2net} \\
\end{split}
\end{equation}
%T_{tot} = T_{RU} + T_{front} + T_{DU} + T_{mid} + T_{CU} + T_{back} + T_{core} + T_{trans2net}
Total delay is sum of processing delay, transmission delay and propagation delay. 
The propagation delay is the time takes for a signal to reach to its destination. So it has a constant value based on the length of fiber link ($T = L/C_{r}$, where $L$ is the length of link and $C_{r}$ is the capacity of the link).
Here we assume the value of propagation delay is negligible compared to the rest.
\subsubsection{Processing Delay}
Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u(s,i)}$ for the $i^{th}$ UE of the $s^{th}$ slice.
Therefore, the mean arrival data rate of the $s^{th}$ slice in the UPF layer is $\alpha_{s}^1 = \sum_{u=1}^{U_s}a_{u(s,i)}\lambda_{u(s,i)}$, where $a_{u(s,i)}$ is a binary variable which indicates whether the $i^{th}$ UE requested $s^{th}$ service is admitted or not.

@@

\subsection{Power of the O-RU and the Fronthaul Capacity}
Let $P_r$ denote the power of the transmitted signal from the $r^{th}$ O-RU to UEs served by it. From \eqref{eq2}, we have,
\begin{equation}\label{pr}
P_r = \sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}+ \sigma_{q}^2.
Since we have a fiber link between O-RU and O-DU, the rate of users on the fronthual link between O-DU and the $r^{th}$ O-RU  is formulated as
%\cite{simeone2016cloud, 1111}
\begin{equation}\label{cr}
C_{r} = \log{\left(1+ \frac{\sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 \mathcal{\alpha}^k_{r,u(s,i)} }{ \sigma_{q}^2}\right)},
where $\mathcal{\alpha}^k_{r,u(s,i)}= p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}$ and $\sigma_{q}^2$ is the power of quantization noise.

@@
